{\bf Demystifying Debugging}

### 2012-11-06 gpi-debug/debugging.tex
more debug

\newcommand\linegap{\vspace{0.2in}}
\newcommand\breakslide[1]{\begin{frame}{} \begin{center} \Large #1 \end{center} \end{frame}}
\newcommand\related[1]{\textsuperscript{\em [#1]}}
\newcommand\hilight[2]{\color{#1}#2\color{black}}

@@

\begin{frame}{The Essence of Debugging}
	...is {\bf telling a good story.}
	\pause
	\linegap
	Two stories, actually:
	\begin{itemize}
		\item What you wanted to happen
		\item What the computer actually did
	\end{itemize}
	\pause
	Your bug: The point where the stories diverge
	\begin{itemize}
		\item Can you describe that point in as much detail as possible?
	\end{itemize}
\end{frame}

@@

\begin{frame}{Running Example}
	% TODO
\end{frame}

@@

\begin{frame}{Telling a Story of Time}
	Remember, two stories: Expected outcome vs Actual outcome
	\linegap
	What does this mean 
	% Text: "First I ... then I ... but then it ...!"
\end{frame}

@@

\begin{frame}{Telling a Story of Space}
	Remember, two stories: Expected outcome vs Actual outcome
	\linegap
\end{frame}

>>>>

\newcommand\linegap{\vspace{0.2in}}
\newcommand\breakslide[1]{\begin{frame}{} \begin{center} \Large #1 \end{center} \end{frame}}
\newcommand\related[1]{\textsuperscript{\em [#1]}}
\newcommand\hilight[2]{\color{#1}#2\color{black}}
\definecolor{grey}{RGB}{127,127,127}
\definecolor{darkcyan}{RGB}{0,127,127}
\definecolor{olivegreen}{RGB}{0,127,0}
\definecolor{violet}{RGB}{127,0,127}
\definecolor{brickred}{RGB}{127,0,0}
\definecolor{brown}{RGB}{127,63,0}

@@

\begin{frame}{The Essence of Debugging}
	...is {\bf telling a good story.}
	\pause
	\linegap

	Two stories, actually:
	\begin{itemize}
		\item What you wanted to happen
		\item What the computer actually did
	\end{itemize}
	\pause
	Your bug: The point where the stories diverge
	\begin{itemize}
		\item Can you describe that point in as much detail as possible?
	\end{itemize}
\end{frame}

@@

\begin{frame}{Running Example}
	\textbf{Broken \texttt{insert\_sorted}}

	\linegap
	Sorts OK into the middle and front of list:
	\begin{itemize}
		\item \texttt{insert\_sorted} $\quad \hilight{olivegreen}{10} \quad  [20,30] \quad \Rightarrow \quad [\hilight{olivegreen}{10},20,30]$
		\item \texttt{insert\_sorted} $\quad \hilight{olivegreen}{32} \quad  [16,64] \quad \Rightarrow \quad [16,\hilight{olivegreen}{32},64]$
	\end{itemize}

	\linegap
	But not so great at the end:
	\begin{itemize}
	\item \texttt{insert\_sorted} $\quad \hilight{red}{100}  \quad [97,98,99] \quad \Rightarrow \quad [97,98,\hilight{red}{100},99]$
	\end{itemize}
\end{frame}

\begin{frame}{Running Example}
	\textbf{Broken \texttt{insert\_sorted}}

	\linegap
	In case you're curious, here's the bug:

	\linegap
		\texttt{~~~~insert\_sorted(list,~element)~\{} \\
			\texttt{~~~~~~~~\hilight{olivegreen}{int}~i~=~\hilight{brickred}{0};} \\
		\texttt{~~~~~~~~\hilight{brown}{while}~(i~<~length(list))~\{~\hilight{darkcyan}{//~Should~be~"<="!}} \\
		\texttt{~~~~~~~~~~~~\hilight{brown}{if}~(element~<~list[i])~\{} \\
		\texttt{~~~~~~~~~~~~~~~~\hilight{brown}{break};} \\
		\texttt{~~~~~~~~~~~~\}} \\
		\texttt{~~~~~~~~\}} \\
		\texttt{~~~~~~~~insert\_at\_index(list,~element);} \\
		\texttt{~~~~\}} \\
\end{frame}

\begin{frame}{Running Example}
	\textbf{Broken \texttt{insert\_sorted}}

	\linegap
	Here is a bad test case. How can we improve it?

	\linegap
		\texttt{~~~~test\_insert\_sorted()~\{} \\
		\texttt{~~~~~~~~input~=~\hilight{brickred}{[99,~42,~3,~100,~87,~56,~22]};} \\
		\texttt{~~~~~~~~output~=~\hilight{brickred}{[]};} \\
		\texttt{~~~~~~~~\hilight{brown}{foreach}~element~\hilight{brown}{in}~input~\{} \\
		\texttt{~~~~~~~~~~~~insert\_sorted(output,~element);} \\
		\texttt{~~~~~~~~\}} \\
		\texttt{~~~~~~~~\hilight{brown}{return}~is\_sorted(output);} \\
		\texttt{~~~~\}} \\
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Strategies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{frame}{Telling a Story of Time}
	Remember, two stories: Expected outcome vs Actual outcome

	\linegap
	What does this mean 
	% Text: "First I ... then I ... but then it ...!"
\end{frame}

@@

\begin{frame}{Telling a Story of Space}
	Remember, two stories: Expected outcome vs Actual outcome

	\linegap
\end{frame}
